\textbf{Computational Fuzzy Extractors}

### 2013-02-15 CompFuzzExt.tex
sketches -> conductor

\subsection{Defining Noisy Computational Conductors}
\label{sec:unp secure sketch}
In \secref{sec:imp HILL sketch}, we showed that defining a computational secure sketch using HILL entropy connects the parameters to the best information-theoretic sketches.  The basic problem is that an adversary had access to both $X$ and $SS(X)$ and could test if neighborhoods correctly decoded.  However, our sketch outputs a new random variable, this problem does not occur.  Instead of building a computational sketch, we will build a computational conductor.  We adapt the definition of a noisy conductor from~\cite{KanukurthiR09} to the computational setting:
%\begin{definition}\protect{\cite[Definition]{KanukurthiR09}}
%The procedures $(\sketch, \rec)$ are an $(\mathcal{M}, m, \tilde{m},t, \epsilon)$-\emph{weakly robust fuzzy conductor} if:
%\begin{enumerate}
%\item Error Tolerance: If $\dis(w, w')\leq t$ and $s\leftarrow \sketch(w)$, then $\Pr[\rec(w', \sketch(w)) \neq  \rec(w, \sketch(w))] \leq \epsilon$ where the probability is over the coins of $\sketch, \rec$.
%\item Security of $\sketch$: If $H_\infty(W) \geq m$, then $\Hav(\rec(W, \sketch(W)) | \sketch(W))\geq \tilde{m}$.
%\end{enumerate}
%\end{definition}
%We will essentially build %if we define the secure sketch using unpredictability entropy~\cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}, this oracle is not available to the adversary.  We begin by defining unpredictability entropy:

%\begin{definition}
%\label{def:unp entropy}
%For a distribution $(X, Z)$, we say that $X$ has unpredictability entropy at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\forall D\in \mathcal{D}_{s_{sec}}, \delta^D((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
%\[
%\Pr[C(Z) = Y ] \leq 2^{-k}
%.\]
%\end{definition}
%We now provide a definition of a robust computational sketch using unpredictability entropy:
\begin{definition}\label{def:comp secure sketch}
A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{noisy computational conductor} is a pair of randomized procedures, sketch (\sketch) and recover (\rec), with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$ and runs in expected time $s_{sketch}$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $d(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))\neq \rec(w, \sketch(w))] = \delta$ and \rec runs in expected time $s_{rec}$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.  
\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the output $\rec$ has high HILL entropy given $\sketch(W)$.  That is, $H^{\hill}_{\epsilon, s_{sec}}(\rec(W, \sketch(W))|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
We say that $(\sketch, \rec)$ is $(\epsilon, s_{sec})$ hard with error probability $\delta$.
If $m=\tilde{m}$ we say a conductor is \emph{lossless} and we omit the parameter $\tilde{m}$.
\end{definition}
%We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.  
In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a noisy computational conductor that meets \defref{def:comp secure sketch}.  We show in the next section that a lossless construction is achievable for the uniform distribution using the LWE problem.

@@

$\mathcal{I}_t$ is an efficient inverter/recovery procedure when $t$ is small enough.  Our inverter will only succeed if it can verify it has the proper $X$. Consider a relation $R(X, (\vA, \vA X+W-W'))$ that verifies if $X$ is the point encoded in $\vA X+W-W'$.   If $n$ is large enough and if $|W-W'|_1$ is small enough, $R$ is a unique witness relation with high probability~(see \defref{def:unique witness relation}) and computable in time $O(n^3)$.
We consider the setting where the running time of $\mathcal{I}_t$ grows with $t$.
%  We provide the results in \lemref{lem:i t constant time} and \lemref{lem:i t poly time} respectively~(proofs in Sections~\ref{sec:proof lem i t constant time},~\ref{sec:proof lem i t poly time}).  \lnote{can we combine these lemmas into one?  It's hard for the reader to compare line-by-line to see where the differences are.  More errors seems better; we could simply point out that constant number of erros leads to better running time, right in the statement of the lemma or right after it}
%\begin{lemma}[Efficiency of $\mathcal{I}_t$ when $t\leq m/n-1$]
%\label{lem:i t constant time}
%Let $\vA, \vA X+E$ be a  $(n,m, q, \chi)$-LWE instance that is a unique witness relation~(except with negligible probability).  Assume $d(E, E')\leq t$ where $t \leq (m-n)/n$.  Then $\mathcal{I}_t$ runs in expected time $O(n^3\log q+ s_{ver})$ on input distribution $\vA, \vA X+E - E'$ and outputs $X' =X$ for all but a negligible fraction of inputs over $\vA, \vA X+E - E'$.
%\end{lemma}
\begin{lemma}[Efficiency of $\mathcal{I}_t$ when $t\leq d\log n (m/n-1)$]
\label{lem:i t poly time}
Let $\vA, \vA X+W$ be a  $(n,m, q, \chi)$-LWE instance that is a unique witness relation~(except with negligible probability).  Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$.  Let $d$ be a constant and assume that $\dis(W, W')\leq t$ where $t\leq d\log n(m/n-1)$.  Then $\mathcal{I}_t$ runs in expected time $O(n^{2d}(n^3\log q))$ on input distribution $\vA, \vA X+W - W'$ and outputs $W$ for all but a negligible fraction of inputs over $\vA, \vA X+W - W'$.
\end{lemma}
\textbf{Note:} If we consider the setting where $t\leq m/n-1$, then $\mathcal{I}_t$ will run in expected time $O(n^3\log n)$.  Our main theorems apply when $t\leq m/n$ with slightly better parameters.  We concentrate on the setting $t\leq d\log n(m/n-1)$.  Also even though we are correcting $O(\log n)$ errors, this a super polynomial number of error patterns and the running time of $\mathcal{I}_t$ is significantly better than exhaustive search over these error patterns.

@@

We now study \consref{cons:informal construction} with a symbol fixing source.  Obviously, if $\alpha \geq n$ then the adversary knows $n$ equations with no error and $W$ can be recovered with Gaussian elimination.  We show that security degrades exponentially as symbols are fixed.
\ignore{
\begin{assumption}[LWE w/ entropic errors]
Let $n$ be a security parameter and define $m = \poly(n)$ and $q\geq 2$ be integers.  Let $W = W_1||...||W_{m+\alpha}$ be a $m$-block fixing distribution over $\{0,1\}^{(m+\alpha)\ell}$. For a vector 
Let $A\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and let $x\in\Fq^{n+\alpha}$.  No PPT algorithm given $Ax+W$ can recover $x$ with probability greater than nonnegligible.
\end{assumption}
}
We now define the decisional $\LWE$ problem with symbol fixing errors is defined as follows: 
\begin{problem}[$\distLWE$ w/ symbol fixing errors]
Let $n$ be a security parameter and define $m = \poly(n)$ and $q\geq 2$ be integers.  Let $W = W_1||...||W_{m+\alpha}$ be a $m$-symbol fixing distribution over $\{0,1\}^{(m+\alpha)b}$. For a vector $X \leftarrow \Fq^n$, we denote $A_{X, W}$ be the distribution obtained by choosing a uniform $\vA\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and output $\vA X + W$. The decisional learning with error problem $\distLWE_{n+\alpha, m+\alpha, q, W}$ is to distinguish samples chosen according $A_{X, W}$ for a uniformly random $X \in \Fq^{n+\alpha}$ from samples chosen according to the uniform distribution over $\Fq^{n+\alpha} \times \Fq$.
\end{problem}

>>>>

\subsection{Defining Noisy Computational Conductors}
\label{sec:unp secure sketch}
In \secref{sec:imp HILL sketch}, we showed that defining a noisy computational conductor using HILL entropy connects the parameters to the best information-theoretic sketches.  The basic problem is that an adversary had access to both $X$ and $SS(X)$ and could test if neighborhoods correctly decoded.  However, our sketch outputs a new random variable, this problem does not occur.  Instead of building a computational sketch, we will build a computational conductor.  We adapt the definition of a noisy conductor from~\cite{KanukurthiR09} to the computational setting:
%\begin{definition}\protect{\cite[Definition]{KanukurthiR09}}
%The procedures $(\sketch, \rec)$ are an $(\mathcal{M}, m, \tilde{m},t, \epsilon)$-\emph{weakly robust fuzzy conductor} if:
%\begin{enumerate}
%\item Error Tolerance: If $\dis(w, w')\leq t$ and $s\leftarrow \sketch(w)$, then $\Pr[\rec(w', \sketch(w)) \neq  \rec(w, \sketch(w))] \leq \epsilon$ where the probability is over the coins of $\sketch, \rec$.
%\item Security of $\sketch$: If $H_\infty(W) \geq m$, then $\Hav(\rec(W, \sketch(W)) | \sketch(W))\geq \tilde{m}$.
%\end{enumerate}
%\end{definition}
%We will essentially build %if we define the secure sketch using unpredictability entropy~\cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}, this oracle is not available to the adversary.  We begin by defining unpredictability entropy:

%\begin{definition}
%\label{def:unp entropy}
%For a distribution $(X, Z)$, we say that $X$ has unpredictability entropy at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\forall D\in \mathcal{D}_{s_{sec}}, \delta^D((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
%\[
%\Pr[C(Z) = Y ] \leq 2^{-k}
%.\]
%\end{definition}
%We now provide a definition of a robust computational sketch using unpredictability entropy:
\begin{definition}\label{def:comp secure sketch}
A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{noisy computational conductor} is a pair of randomized procedures, sketch (\sketch) and recover (\rec), with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$ and runs in expected time $s_{sketch}$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $d(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))\neq \rec(w, \sketch(w))] = \delta$ and \rec runs in expected time $s_{rec}$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.  
\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the output $\rec$ has high HILL entropy given $\sketch(W)$.  That is, $H^{\hill}_{\epsilon, s_{sec}}(\rec(W, \sketch(W))|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
We say that $(\sketch, \rec)$ is $(\epsilon, s_{sec})$ hard with error probability $\delta$.
If $m=\tilde{m}$ we say a conductor is \emph{lossless} and we omit the parameter $\tilde{m}$.
\end{definition}
%We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.  
In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a noisy computational conductor that meets \defref{def:comp secure sketch}.  We show in the next section that a lossless construction is achievable for the uniform distribution using the $\LWE$ problem.

@@

$\mathcal{I}_t$ is an efficient inverter/recovery procedure when $t$ is small enough.  Our inverter will only succeed if it can verify it has the proper $X$. Consider a relation $R(X, (\vA, \vA X+W-W'))$ that verifies if $X$ is the point encoded in $\vA X+W-W'$.   If $n$ is large enough and if $|W-W'|_1$ is small enough, $R$ is a unique witness relation with high probability~(see \defref{def:unique witness relation}) and computable in time $O(n^3)$.
We consider the setting where the running time of $\mathcal{I}_t$ grows with $t$.
%  We provide the results in \lemref{lem:i t constant time} and \lemref{lem:i t poly time} respectively~(proofs in Sections~\ref{sec:proof lem i t constant time},~\ref{sec:proof lem i t poly time}).  \lnote{can we combine these lemmas into one?  It's hard for the reader to compare line-by-line to see where the differences are.  More errors seems better; we could simply point out that constant number of erros leads to better running time, right in the statement of the lemma or right after it}
%\begin{lemma}[Efficiency of $\mathcal{I}_t$ when $t\leq m/n-1$]
%\label{lem:i t constant time}
%Let $\vA, \vA X+E$ be a  $(n,m, q, \chi)$-LWE instance that is a unique witness relation~(except with negligible probability).  Assume $d(E, E')\leq t$ where $t \leq (m-n)/n$.  Then $\mathcal{I}_t$ runs in expected time $O(n^3\log q+ s_{ver})$ on input distribution $\vA, \vA X+E - E'$ and outputs $X' =X$ for all but a negligible fraction of inputs over $\vA, \vA X+E - E'$.
%\end{lemma}
\begin{lemma}[Efficiency of $\mathcal{I}_t$ when $t\leq d\log n (m/n-1)$]
\label{lem:i t poly time}
Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance that is a unique witness relation~(except with negligible probability).  Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$.  Let $d$ be a constant and assume that $\dis(W, W')\leq t$ where $t\leq d\log n(m/n-1)$.  Then $\mathcal{I}_t$ runs in expected time $O(n^{2d}(n^3\log q))$ on input distribution $\vA, \vA X+W - W'$ and outputs $W$ for all but a negligible fraction of inputs over $\vA, \vA X+W - W'$.
\end{lemma}
\textbf{Note:} If we consider the setting where $t\leq m/n-1$, then $\mathcal{I}_t$ will run in expected time $O(n^3\log n)$.  Our main theorems apply when $t\leq m/n$ with slightly better parameters.  We concentrate on the setting $t\leq d\log n(m/n-1)$.  Also even though we are correcting $O(\log n)$ errors, this a super polynomial number of error patterns and the running time of $\mathcal{I}_t$ is significantly better than exhaustive search over these error patterns.

@@

We now study \consref{cons:informal construction} with a symbol fixing source.  Obviously, if $\alpha \geq n$ then the adversary knows $n$ equations with no error and $W$ can be recovered with Gaussian elimination.  We show that security degrades exponentially as symbols are fixed.
\ignore{
\begin{assumption}[LWE w/ entropic errors]
Let $n$ be a security parameter and define $m = \poly(n)$ and $q\geq 2$ be integers.  Let $W = W_1||...||W_{m+\alpha}$ be a $m$-block fixing distribution over $\{0,1\}^{(m+\alpha)\ell}$. For a vector 
Let $A\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and let $x\in\Fq^{n+\alpha}$.  No PPT algorithm given $Ax+W$ can recover $x$ with probability greater than nonnegligible.
\end{assumption}
}
We now define the decisional $\LWE$ problem with symbol fixing errors is defined as follows: 
\begin{problem}[$\distLWE$ w/ symbol fixing errors]
Let $n$ be a security parameter and define $m = \poly(n)$ and $q\geq 2$ be integers.  Let $W = W_1||...||W_{m+\alpha}$ be a $m$-symbol fixing distribution over $\{0,1\}^{(m+\alpha)b}$. For a vector $X \leftarrow \Fq^n$, we denote $A_{X, W}$ be the distribution obtained by choosing a uniform $\vA\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and output $\vA X + W$. The decisional learning with error problem $\distLWE_{n+\alpha, m+\alpha, q, W}$ with symbol fixing errors is to distinguish samples chosen according $A_{X, W}$ for a uniformly random $X \in \Fq^{n+\alpha}$ from samples chosen according to the uniform distribution over $\Fq^{n+\alpha} \times \Fq$.
\end{problem}
